Can Meaning Travel? The Causal Effect of Media Frames on Issue Definitions and Attitudes

### 2021-09-25 paper/main.tex

% show distribution of p-values vs theoretical distribution -> looks like there is systematic deviation

@@

% show correlation of DiD with prevalence of media frames (STM)

>>>>

% show distribution of p-values vs theoretical distribution -> looks like there is systematic deviation
\begin{figure}[!ht]
    \centering
    \includegraphics[width=\textwidth]{paper/vis/DiD_model_ps.png}
    \caption{Empirical and theoretical p-values of 1,363 DiD-models.}
    \label{fig:p_values}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\textwidth]{paper/vis/frames_papers_wtd.png}
    \caption{Prevalence of different migration frames across newspapers. Gray vertical lines indicate survey field dates.}
    \label{fig:frames}
\end{figure}

% show correlation of DiD with prevalence of media frames (STM)
\begin{figure}[!ht]
    \centering
    \includegraphics[width=\textwidth]{paper/vis/effectplot_noimp.png}
    \caption{Correlation of opinion shifts (DiDs) with media attention or shifts in attention (DiD's) for different specifications. Note that immigration and integration are inversely coded. Higher values indicate more restrictive attitudes on immigration, but more liberal attitudes on integration. Signs indicate the hypothesized effect of the frame on integration.}
    \label{fig:did_corr}
\end{figure}
